Untitled

### 2019-01-18 sandbox_animation_tas.Rmd
Australia and Tasmania Animations

---
title: "Australia"
author: "Stephanie"
date: "15/01/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

# Select only desired LGA areas, those from ausmania.
lga_2011[[sf_id]] <- droplevels(as.factor(lga_2011[[sf_id]]))

## Not necessary when using `create_hexmap`:
## Derive projection information
crs_info <- sf::st_crs(lga_2011)
proj4string <- crs_info$proj4string
epsg <- crs_info$epsg

@@

lga_2011 <- lga_2011 %>%
    sf::st_transform(., crs = projstring)

```

```{r}
# Change this for a more detailed map
fort_aus <- fortify_sfc(lga_2011, projstring = projstring, simplify = 0.2)
```

@@

lga_map <- create_hexmap(shp = lga_2011, sf_id = "LGA_CODE11", buffer_dist = NULL, filter_dist = 10, hex_size = hex_size, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)

hexmap_lga <- left_join(lga_2011, 
  lga_map)
```

@@

# variable data
areasq <- bind_cols(LGA_CODE11 = lga_2011$LGA_CODE11, 
  area = lga_2011$AREA_SQKM)

hex_verts <-  hex_points_df %>%
  left_join(areasq) %>% 
  mutate(point_type = "hex") %>% 
  left_join(fort_aus %>% 
      dplyr::select(LGA_CODE11, group) %>%
      mutate(group = group))

geo_verts <- fort_aus %>% dplyr::select(LGA_CODE11, long, lat, group, order, area = AREA_SQKM) %>% 
  mutate(point_type = "polygon") %>%
  left_join(hex_verts %>% 
    dplyr::select(LGA_CODE11, hex_id) %>% distinct())

@@

# Create static plot
ggplot(hex_animate) + 
  geom_polygon(aes(x = long, y = lat, group = group)) + facet_wrap(~point_type) + coord_equal()
ggplot() +geom_sf(data = lga_2011)
```

>>>>

---
title: "Untitled"
author: "Stephanie"
date: "15/01/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

# Select only desired LGA areas, those from tasmania.
tas_lga <- lga_2011 %>% filter(STE_NAME11 == "Tasmania")
tas_lga[[sf_id]] <- droplevels(as.factor(tas_lga[[sf_id]]))

## Not necessary when using `create_hexmap`:
## Derive projection information
crs_info <- sf::st_crs(tas_lga)
proj4string <- crs_info$proj4string
epsg <- crs_info$epsg

@@

tas_lga <- tas_lga %>%
    sf::st_transform(., crs = projstring)

## Use the create_centroids function to find polygon centroids:
#centroids <- create_centroids(shp_sf = tas_lga, sf_id = sf_id, projstring = projstring, verbose = FALSE)

# Change this for a more detailed map
fort_tas <- fortify_sfc(tas_lga, projstring = projstring, simplify = 1)
```

@@

lga_map <- create_hexmap(shp = tas_lga, sf_id = "LGA_CODE11", buffer_dist = NULL, filter_dist = 10, hex_size = hex_size, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)

hexmap_lga <- left_join(tas_lga, 
  lga_map)
```

@@

# variable data
areasq <- bind_cols(LGA_CODE11 = tas_lga$LGA_CODE11, 
  area = tas_lga$AREA_SQKM)

hex_verts <-  hex_points_df %>%
  left_join(areasq) %>% 
  mutate(point_type = "hex") %>% 
  left_join(fort_tas %>% 
      dplyr::select(LGA_CODE11, group) %>%
      mutate(group = group))

geo_verts <- fort_tas %>% dplyr::select(LGA_CODE11, long, lat, group, order, area = AREA_SQKM) %>% 
  mutate(point_type = "polygon") %>%
  left_join(hex_verts %>% 
    dplyr::select(LGA_CODE11, hex_id) %>% distinct())

@@

# Create static plot
ggplot(hex_animate) + 
  geom_polygon(aes(x = long, y = lat, group = group)) + facet_wrap(~point_type) + coord_equal()
ggplot() +geom_sf(data = tas_lga)
```
